DeepRain

### 2019-08-25 Docs/Langdokumentation.tex
Paket für Anführungszeichen durch eigenen Befehl ersetzt; Readme für Crawler
Abkürzungsverzeichnis

\usepackage[english,ngerman]{babel}                 % German and English word separation settings
\usepackage[autostyle=true,german=quotes]{csquotes} % Better German quotes
\usepackage{graphicx}  
\usepackage{float}                             % Include graphics/images
\usepackage{multirow}                               % Row spanning over multiple rows
\usepackage{subcaption}                             % Used for 2 images side-by-side
\usepackage{tabularx} % for 'tabularx' environment
\usepackage[bookmarks,                 % Creates bookmarks
            bookmarksnumbered=true,    % Numbers in PDF bookmarks
            bookmarksopen=true,        % Don't show bookmaks when opened
            hyperindex=true,           % Numbers in index are links
            pdfpagelabels=true,        % Set PDF page labels
            pdfa]{hyperref}                         % Klickable Links and ToC entries (should be last package !!!)

@@

>>>>

\usepackage[english,ngerman]{babel}                 % German and English word separation settings
\newcommand{\gqq}[1]{\glqq #1\grqq{}}               % Own command for german quotes
\usepackage{graphicx}                               % Include graphics/images
\usepackage{float}
\usepackage{multirow}                               % Row spanning over multiple rows
\usepackage{subcaption}                             % Used for 2 images side-by-side
\usepackage{tabularx}                               % for 'tabularx' environment
\usepackage[printonlyused,withpage]{acronym}        % Abkürzungsverzeichnis, https://de.wikibooks.org/wiki/LaTeX-W%C3%B6rterbuch:_Abk%C3%BCrzungsverzeichnis
\usepackage[bookmarks,                 % Creates bookmarks
            bookmarksnumbered=true,    % Numbers in PDF bookmarks
            bookmarksopen=true,        % Don't show bookmaks when opened
            hyperindex=true,           % Numbers in index are links
            pdfpagelabels=true,        % Set PDF page labels
            pdfa]{hyperref}                         % Klickable Links and ToC entries (should be last package !!!)

@@

\begin{acronym}[Bash] % Hier steht die längste Abkürzung, damit die Breite stimmt
 \acro{DL}{Deep Learning}
 \acro{Bash}{Bourne-again shell}
 \acro{VM}{Virtuelle Maschine}
\end{acronym}
